ANGSD-wrapper: utilities for analyzing next generation sequencing data

### 2016-01-20 manuscript.tex
added trip coverage

As a demonstration of analyses in ANGSD-wrapper, we explore patterns of diversity in a single genomic region of domesticated maize and wild teosinte. 
We used a subset of the resequenced samples from the Maize HapMap2 project (Table \ref{tab:samples}) \jri{please add Tripsacum to this table and add species identity to the table} and calculated summary statistics using a 10 megabase region on chromosome 10 \citep{chia2012maize}. The data are available at \url{https://figshare.com/articles/Example_Data_tar_bz2/2063442}. In the following we refer to methods listed in Table \ref{tab:methods} when describing analyses.

>>>>

As a demonstration of analyses in ANGSD-wrapper, we explore patterns of diversity in a single genomic region of domesticated maize and wild teosinte. 
We used a subset of the resequenced samples from the Maize HapMap2 project (Table \ref{tab:samples}) and calculated summary statistics using a 10 megabase region on chromosome 10 \citep{chia2012maize}. The data are available at \url{https://figshare.com/articles/Example_Data_tar_bz2/2063442}. In the following we refer to methods listed in Table \ref{tab:methods} when describing analyses.
